`tidyfun`

### 2021-04-20 papers.Rmd
update papers and CV

D. Backenroth<sup>&#8224;</sup>, R. T. Shinohara, J. A. Schrack, and **J. Goldsmith** (2020+).
Non-negative decomposition of functional count data. 
<i> Biometrics, </i>  accepted.

A. E. Margolis, J. Broitman, J. M. Davis, L. Alexander, A. Hamilton, Z. Liao, S. Banker, L. Thomas, G. A. Salum, K. Merikangis, **J. Goldsmith**, T. Paus, K. Keyes, M. P. Milham (2020+).
Prevalence Of Nonverbal Learning Disability In Three Community Samples
<i> JAMA Network Open, </i> accepted.

D. Pagliaccio et al (2020+).
Prenatal Exposure to Polycyclic Aromatic Hydrocarbons Modifies the Effects of Early Life Stress on Attention & Thought Problems in Late Childhood.
<i> The Journal of Child Psychology and Psychiatry,, </i> accepted.

>>>>

D. Backenroth$^\ddagger$, R. T. Shinohara, J. A. Schrack, and **J Goldsmith** (2020).
	Non-negative decomposition of functional count data. 
	<i> Biometrics, </i> 
	<b>76</b> 1273-1284.
	[[Link](https://onlinelibrary.wiley.com/doi/abs/10.1111/biom.13220)]

J Wrobel$^\ddagger$, ML Martin, R Bakshi, PA Calabresi, M Elliot, D Roalf, RC Gur, RE Gur, RG Henry, G Nair, J Oh, N Papinutto, D Pelletier, Daniel Salo Reich, WD Rooney, TD Satterthwaite, W Stern, K Prabhakaran, NL Sicotte, RT Shinohara, \bf J. Goldsmith \rm (2020).
	Intensity warping for multisite MRI harmonization.
	<i> NeuroImage, </i> 
	<b>223</b> 117284.

D Pagliaccio, JB Herbstman, F Perera, D Tang, J Goldsmith, BS Peterson, V Rauh, AE and Margolis (2020). 
  Prenatal exposure to polycyclic aromatic hydrocarbons modifies the effects of early life stress on attention and Thought Problems in late childhood. 
  <i> Journal of Child Psychology and Psychiatry, </i> 
  <b>61</b> 1253-1265.

J M Griffin, L Chiu, K M Axsom, R Bijou, K J Clerkin, P Colombo, M O Cuomo, J De Los Santos, J A Fried, **J Goldsmith**, M Habal, J Haythe, S Helmke, E M Horn, F Latif, S H Lee, E F Lin, Y Naka, J Raikhelkar, S Restaino, G T Sayer, H Takayama, K Takeda, S Teruya, V Topkara, E J Tsai, N Uriel, M Yuzefpolskaya, M A Farr, M S Maurer (2020).
	United network for organ sharing outcomes after heart transplantation for al compared to ATTR cardiac amyloidosis	
	<i> Annals of the American Thoracic Society, </i> 
	<b>34</b> e14028.

L R Mitrani, J De Los Santos, E Driggin, R Kogan, S Helmke, **J Goldsmith**, A B Biviano, M S Maurer (2020). 
	Anticoagulation with warfarin compared to novel oral anticoagulants for atrial fibrillation in adults with transthyretin cardiac amyloidosis: comparison of thromboembolic events and major bleeding
	<i> Amyloid, </i> 
	<b>28</b> 30-34.

H Rosenblum, A Masri, D L Narotsky, **J Goldsmith**, N Hamid, R T Hahn, S Kodali, T Vahl, T Nazif, O K Khalique, S Bokhari, P Soman, J L Cavalcante, M S Maurer, A Castano
	Unveiling outcomes in coexisting severe aortic stenosis and transthyretin cardiac amyloidosis (2020).
	<i> European Journal of Heart Failure, </i> 
	<b>23</b> 250-258.

M He, P Kinney, C Chen, Q Sun, J Ban, J Wang, S Liu,  **J Goldsmith**, M-A Kioumourtzoglou (2020).
	Short- and intermediate- term exposure to NO2 and mortality: a multi-county analysis in China. 
	<i> Environmental Pollution, </i> 
	<b>261</b> 114165.

E Driggin, S Helmke, J De Los Santos, S Teruya, S Guadalupe, **J Goldsmith**, M S Maurer (2020).
	Markers of nutritional status and inflammation in transthyretin cardiac amyloidosis: association with outcomes and the clinical phenotype.
	<i> Amyloid, </i> 
	<b>27</b> 73-80.

A. E. Margolis, J. Broitman, J. M. Davis, L. Alexander, A. Hamilton, Z. Liao, S. Banker, L. Thomas, G. A. Salum, K. Merikangis, **J. Goldsmith**, T. Paus, K. Keyes, M. P. Milham (2020).
Prevalence Of Nonverbal Learning Disability In Three Community Samples
<i> JAMA Network Open, </i> 
<b>3</b> e202551-e202551
